Classical density functional theory for the square-well liquid

### 2015-07-14 papers/square-well-fluid/paper.tex
Added radial distribution plotting for square well fluid. Data is currently junk. Tested on knightley. Took 0:19.59.
add homogeneous p-vs-eta plot for sw dft Tested on knightley. Took 0:24.96.
include coexistence plot in sw paper Tested on darcy. Took 0:59.90.
show g(r) fit figure in sw paper Tested on darcy. Took 1:00.46.
first guess for scalefunction, and add some discussion to sw paper Tested on darcy. Took 2:51.96.

\author{Student One}
\author{Michael A. Perlin}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

@@

@@

A different way to do this that avoids some of the Fourier transform
troubles is to formulate $g_S$ as a polynomial expansion.  We do this
up to fouth order so that
\begin{align}
  g_S(r;g_\sigma) &= g_\sigma + \sum_i \gamma_i(g_\sigma) \xi_i(r) \\
  &=
  g_\sigma + \sum_{i=1}^{4} \left(\sum_{j=1}^{4} (g_\sigma
  - 1)^j \kappa_{ji} \right)
  \left(\frac{r}{\sigma}-1\right)^i,
  \label{eq:fit-form}
\end{align}
which makes the transforms for $i=1,2,3,4$
\begin{align}
 \frac {4\pi}{k}\int r \xi_i(r) \Phi(r) \sin (kr) \dd r =  \frac
       {-4\pi\epsilon}{k}\int_\sigma^{\lambda \sigma} r \xi_i(r)\sin (kr) \dd r
\end{align}
For the ``zeroth'' term, we treat it like $\xi=1$, so that we're only
transforming the potential well.
%% For the other i's, we'll do a
%% u-substitution where $u= \frac{r}{\sigma}-1$, then the
%% integral becomes
%% \begin{align}
%%  \frac {4\pi}{k}\int_0^{\lambda -1} \sigma^2 (u+1)u^i \sin(k\sigma
%%        [u+1]) \mathrm{d}u.
%% \end{align}
%% Now we calculate the integrals.
\begin{widetext}
\begin{align}
  \int_\sigma^{\lambda \sigma} r \sin (kr) \mathrm{d}r =&
  \frac{1}{k^2}\left[ \sin (k\lambda\sigma) - k\lambda\sigma
    \cos (k\lambda\sigma) - \sin (k\sigma) + k\sigma \cos (k-sigma) \right]\\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right) \sin (kr) \mathrm{d}r =&
 \frac{1}{k^3 \sigma}\left[(2-\lambda k^2
 \sigma^2(\lambda-1))\cos(k\lambda\sigma)-k\sigma(\sin(k\sigma)
 +(1-2\lambda) \sin(k\lambda\sigma)) -\cos(k\sigma) \right] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^2 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^4\sigma^2} \big[
 6\sin(k\sigma)+(k^2\sigma^2(1-4\lambda+3\lambda^2)
 -6)\sin(k\lambda\sigma) \notag \\
 &-2k\sigma\cos(k\sigma) - k\sigma(4 +
 \lambda(k^2\sigma^2(\lambda-1)^2 - 6))\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^3 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^5\sigma^3} \big[k\sigma(6\sin(k\sigma) + (18-24\lambda
   +k^2\sigma^2(\lambda-1)^2(4\lambda-1))\sin(k\lambda\sigma)) \notag \\
   &+24\cos(k\sigma) + (6k^2\sigma^2(\lambda-1)(2\lambda-1)-\lambda
   k^4\sigma^4(\lambda-1)^3)\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^4 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^6\sigma^4}
 \big[(k^2\sigma^2(\lambda-1)(36-60\lambda+k^2\sigma^2(\lambda - 1)^2(5\lambda-1))
   + 120)\sin(k\lambda\sigma) - 120\sin(k\sigma) \notag \\
   &+k\sigma(24\cos(k\sigma) -
   (24(5\lambda-4)-4k^2\sigma^2(\lambda-1)^2 (5\lambda-2) +
   \lambda k^4\sigma^4(\lambda-1)^4))\cos(k\lambda\sigma) \big]
\end{align}
\end{widetext}
\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}

@@

>>>>

\author{Eric Krebs}
\author{Michael A. Perlin}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

@@

\subsection{FIXME fit for g(r)}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/short-range-ghs-alt}
  \end{center}
  \caption{g(r) fit.}
  \label{fig:gr}
\end{figure}

We have found a problem with the pair distribution function developed
in reference~\citenum{lurie2014approach}, which is that this pair
distribution function can diverge as the contact value of the pair
distribution function $g_\sigma$ diverges, as happens at high
densities.  While the published pair distribution function does
provide a good approximation at reasonable densities, this divergence
causes functionals constructed with it to exhibit non-physical
densities.  We have fixed this problem by modifying the
pair distribution function at densities at which the hard-sphere fluid
is crystalline.

\input{figs/short-range-fit-parameters}

\begin{table}
  \begin{align*}
    \kappa &= \kappatable
  \end{align*}
  \caption{The fitted $\kappa_{ij}$ matrix.  Note that the first
    column of $\kappa$ corresponds to $j=1$ while the first row
    corresponds to $i=1$ in Eq.~\ref{eq:kappa-defined}.  }\label{tab:kappa}
\end{table}

I should write more about the form of the fit, or move this where
appropriate.  We have performed a modified fit to the Monte Carlo
radial distribution function using the following functional form
\begin{align}
  g_S(r;g_\sigma) &=  1 + \sum_i \gamma_i(g_\sigma) \left(\frac{r}{\sigma}-1\right)^i,
  \label{eq:new-fit-form}
\end{align}
where the polynomial coefficients in $g_S(r;g_\sigma)$ have the
following dependency on $g_\sigma$:
\begin{equation}
  \gamma_i(g_\sigma) = f(g_\sigma)
  \begin{cases}
    \displaystyle
    g_\sigma - 1 & i = 0 \\
    \displaystyle
    \sum_{j=1}^{4} (g_\sigma
    - 1)^j \kappa_{ji} & i > 0 \label{eq:kappa-defined}
  \end{cases}
\end{equation}
with
\begin{equation}
  f(g_\sigma) = \frac{1 - \tanh(4 \frac{h_\sigma -
      \hsigmastop}{\hsigmastop - \hsigmastart})}{2}
\end{equation}
This function is constructed to quickly approach 1 in the fluid for
where $\eta < \etastart$ and to approach 0 in the crystalline form
where $\eta > \etastop$.  The largest error in this fit (an error of
$\maxerr$) is at the maximum density considered with $\eta =
\etamaxerr$, and is at a distance $r = \rmaxerr R$.  As is
Ref.~\citenum{lurie2014approach}, we constrained our fit to radii less
than $\maxrfit R$, so the maximum error appears at close to the
maximum allowed distance.  We show the fitted values of $\kappa_{ji}$
in Table~\ref{tab:kappa}.

@@

A different way to do this that avoids some of the Fourier transform
troubles is to formulate $g_S$ as a polynomial expansion.  We do this
up to fouth order so that
\begin{align}
  g_S(r;g_\sigma) &= g_\sigma + \sum_i \gamma_i(g_\sigma) \xi_i(r) \\
  &=
  g_\sigma + \sum_{i=1}^{4} \left(\sum_{j=1}^{4} (g_\sigma
  - 1)^j \kappa_{ji} \right)
  \left(\frac{r}{\sigma}-1\right)^i,
  \label{eq:fit-form}
\end{align}
which makes the transforms for $i=1,2,3,4$
\begin{align}
 \frac {4\pi}{k}\int r \xi_i(r) \Phi(r) \sin (kr) \dd r =  \frac
       {-4\pi\epsilon}{k}\int_\sigma^{\lambda \sigma} r \xi_i(r)\sin (kr) \dd r
\end{align}
For the ``zeroth'' term, we treat it like $\xi=1$, so that we're only
transforming the potential well.
%% For the other i's, we'll do a
%% u-substitution where $u= \frac{r}{\sigma}-1$, then the
%% integral becomes
%% \begin{align}
%%  \frac {4\pi}{k}\int_0^{\lambda -1} \sigma^2 (u+1)u^i \sin(k\sigma
%%        [u+1]) \mathrm{d}u.
%% \end{align}
%% Now we calculate the integrals.
\begin{widetext}
\begin{align}
  \int_\sigma^{\lambda \sigma} r \sin (kr) \mathrm{d}r =&
  \frac{1}{k^2}\left[ \sin (k\lambda\sigma) - k\lambda\sigma
    \cos (k\lambda\sigma) - \sin (k\sigma) + k\sigma \cos (k\sigma) \right]\\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right) \sin (kr) \mathrm{d}r =&
 \frac{1}{k^3 \sigma}\left[(2-\lambda k^2
 \sigma^2(\lambda-1))\cos(k\lambda\sigma)-k\sigma(\sin(k\sigma)
 +(1-2\lambda) \sin(k\lambda\sigma)) -2\cos(k\sigma) \right] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^2 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^4\sigma^2} \big[
 6\sin(k\sigma)+(k^2\sigma^2(1-4\lambda+3\lambda^2)
 -6)\sin(k\lambda\sigma) \notag \\
 &-2k\sigma\cos(k\sigma) - k\sigma(4 +
 \lambda(k^2\sigma^2(\lambda-1)^2 - 6))\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^3 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^5\sigma^3} \big[k\sigma(6\sin(k\sigma) + (18-24\lambda
   +k^2\sigma^2(\lambda-1)^2(4\lambda-1))\sin(k\lambda\sigma)) \notag \\
   &+24\cos(k\sigma) + (6k^2\sigma^2(\lambda-1)(2\lambda-1)-\lambda
   k^4\sigma^4(\lambda-1)^3-24)\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^4 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^6\sigma^4}
 \big[(k^2\sigma^2(\lambda-1)(36-60\lambda+k^2\sigma^2(\lambda - 1)^2(5\lambda-1))
   + 120)\sin(k\lambda\sigma) - 120\sin(k\sigma) \notag \\
   &+k\sigma(24\cos(k\sigma) -
   (24(5\lambda-4)-4k^2\sigma^2(\lambda-1)^2 (5\lambda-2) +
   \lambda k^4\sigma^4(\lambda-1)^4)\cos(k\lambda\sigma)) \big]
\end{align}
\end{widetext}
\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/coexistence-ww1_3}
\end{center}
\caption{Pressure.}
\label{fig:coexistencec}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/p-vs-eta}
\end{center}
\caption{Pressure.}
\label{fig:p-vs-eta}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{figs/radial-sw-20}
\end{center}
\caption{RDF.}
\label{fig:homogeneous-20}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{figs/radial-sw-30}
\end{center}
\caption{RDF.}
\label{fig:homogeneous-30}
\end{figure}
